---
title: "p8105_hw1_xw3106"
Author: "Xinyu Wang(xw3106)"
output: github_document
---
#Problem 1

```{r}
library(moderndive)
data("early_january_weather")
```

The dataset "early_january_weather" is the hourly meteorological data for EWR for the month of January in 2013. It have `r nrow(early_january_weather)` observations and `r ncol(early_january_weather)`  variables. The dataset includes variables as listed: `r names(early_january_weather)`. Among them, "year, month, day, hour" are time of the recording,"time_hour" records the date and hour as a POSIXct date. "temp, dewp" are <dbl> that records temperature and dewpoint in F;"wind_dir, wind_speed, wind_gus" records the wind direction (in degrees), speed and gust speed (in mph). The mean temperature is `r mean(early_january_weather$temp, na.rm = TRUE)`.

```{r}
library(ggplot2)

plot1 <- ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point() 
plot1 + labs(title = "Hourly Temperature and Humidity change of January 2013", x = "Time(hour)", y = "Temperature(F)") + scale_x_datetime(date_breaks = "2 day", date_labels = "%b %d")

```
The scatter plot shows the temperature tends to increases during the middle of day and drop at night, and it repeats with a daily cycle. Lower humidity level are associated with temprature decrease from the daily peak. From Jan12-Jan14, temprature remained relatively constant with a high humidity level. After 12pm on Jan 14, humidity dropped sharply followed by a noticeble temperature decrease. 

#Problem 2

```{r}
library(tidyverse)

set.seed(1)

df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0,
  vec_char = letters[1:10],
  vec_factor = factor(c("A","B" ,"A", "B", "B", "C", "B","B" ,"C", "A"))
)
df
```
```{r}
mean(df %>% pull(vec_numeric))
mean(df %>% pull(vec_logical))
mean(df %>% pull(vec_char))
mean(df %>% pull(vec_factor))
```
The mean works for numeric and logical vectors. It does not work on char and factor vectors.

```{r}
as.numeric(df$vec_logical)
as.numeric(df$vec_char)
as.numeric(df$vec_factor)
```

